When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-06-16 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
updated

Following a reviewer's recommendation, we also analyzed the association of SVs with NFC as a continuous variable.
We computed an rmANOVA with the $n$-back level as a within variable and the standardized NFC score as a covariate to predict SVs.
Both the NFC score (`r apa_print(explor2_model)$full_result$nfc`, `r apa_print(explor2_BF_nfc)$statistic`) and the $n$-back level (`r apa_print(explor2_model)$full_result$level`, `r apa_print(explor2_BF_level)$statistic`) showed significant main effects, as well as a significant interaction (`r apa_print(explor2_model)$full_result$nfc_level`, `r apa_print(explor2_BF_interact)$statistic`).
Analyzing the estimated marginal means of the linear trends for each $n$-back level indicated a significant difference between the slopes of 1-back and 4-back (`r apa_print(explor2_slopes$contrasts)$full_result$Level1_level4`), but not between any other two levels.
Plotting the predicted slopes shows that there is a negative association between the predicted SVs and the NFC scores for 1-back, but a positive association between the predicted SVs and the NFC scores for 4-back (Figure\ \@ref(fig:nfccont-sv)).

@@

```{r sv-by-pref, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per $n$-back level, grouped into those who had an absolute preference for 1-back, for 2-back, for 3-back, for 4-back, or no absolute preference for any level. The lines have a vertical jitter of 0.02. Smoothing of conditional means with Loess method. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

>>>>

Following a reviewer's recommendation, we also analyzed the association of SVs with NFC as a continuous variable.
We computed an rmANOVA with the $n$-back level as a within variable and the standardized NFC score as a covariate to predict SVs.
Both the NFC score (`r apa_print(explor2_model)$full_result$nfc`, `r apa_print(explor2_BF_nfc)$statistic`) and the $n$-back level (`r apa_print(explor2_model)$full_result$level`, `r apa_print(explor2_BF_level)$statistic`) showed significant main effects, as well as a significant interaction (`r apa_print(explor2_model)$full_result$nfc_level`, `r apa_print(explor2_BF_interact)$statistic`).
Analyzing the estimated marginal means of the linear trends for each $n$-back level indicated a significant difference between the slopes of 1-back and 4-back (`r apa_print(explor2_slopes$contrasts)$full_result$Level1_level4`), but not between any other two levels.
Plotting the predicted slopes shows that there is a negative association between the predicted SVs and the NFC scores for 1-back, but a positive association between the predicted SVs and the NFC scores for 4-back (Figure\ \@ref(fig:nfccont-sv)).
The full results of this exploratory analysis of NFC as a continuous covariate can be found in Table S.18 and S.19 in the Supplementary Material.

@@

```{r sv-by-pref, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values (SV) per $n$-back level, grouped into those who had an SV = 1 for 1-back, for 2-back, for 3-back, for 4-back, or no SV = 1 for any level. The lines have a vertical jitter of 0.02. Smoothing of conditional means with Loess method. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

### 2023-06-16 06_Paper/COG-ED/Stage 2/Supplement.Rmd
updated

## Exploratory analyses

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  explor_contrasts_interact,
  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on subjectvie values.",
  note = "The column Contrast contains the groups above (high) and below (low) the Need for Cognition score median. The column Level contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

>>>>

## Exploratory analysis with NFC groups by median split

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  explor_contrasts_interact,
  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on subjective values.",
  note = "The column Contrast contains the groups above (high) and below (low) the Need for Cognition score median. The column Level contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

## Exploratory analysis with NFC as a continuous covariate

ANOVA (NFC scores standardized):

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  explor2_rmanova,
  caption = "Result of the rmANOVA regarding the predictive power of the $n$-back level on the subjective values when including Need for Cognition scores as a centered continuous covariate.",
  note = "NFC = Need for Cognition. $SE$ = standard error, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, $\\eta_{p}^{2}$ = partial eta squared, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

Estimated marginal means of the linear trends:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  explor2_emm,
  caption = "Paired contrast slope analysis as a follow up for the rmANOVA regarding the predictive power of the $n$-back level on the subjective values when including Need for Cognition scores as a centered continuous covariate.",
  note = "The column $n$-back level contains the $n$ of the task levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
  escape = FALSE,
  placement = "H"
)
```
